### 2016-10-01 intro.tex
related work

\heading{Comparison to~\cite{naor2015bloom}.} Naor and
Yogev~\cite{naor2015bloom} recently considered the problem of
adversarial soundness for Bloom filters and, indeed,
their worked served as inspiration for our own. Our work extends
their work significantly in several directions. For starters, we
consider abstract data structures (rather than only the case of
set-membership data structures), and consider privacy in addition to
soundness. Even with respect to the specific case of soundness for
set-membership data structures, our work offers several advantages
to the Naor-Yogev treatment:
\begin{itemize}
\item We explicitly distinguish between public and private
    portions of a data structure, something that was left
    ambiguous in~\cite{naor2015bloom}. This allows us, for
    example, to distinguish between the hash-function keys and
    the bit array when discussing classical Bloom filters.
\item The Naor-Yogev definition of soundness allows the
    adversary to make several set-membership queries, some of
    which may produce incorrect results, and the attacker then
    succeeds if it can output a \emph{fresh} query which leads
    to an error. We propose instead what we find to be a more
    natural definition in which the attacker succeeds if it can
    cause a certain number of incorrect results.
\item Naor and Yogev analyze a new Bloom-filter construction of
    their own design. In contrast, we are interested in
    analyzing practical constructions that have been proposed in
    prior work to understand how secure they are. In particular,
    we analyze Bloom filters in the random-oracle model.
    \jnote{Which are widely used?}
\end{itemize}
\tsnote{I think we can say a bit more here about what they show, and
  why their presentation is lacking, certainly as a work that anchors
  an important area of study.  This feels a bit weak, at the moment.
  For example, at the opening of this section we say they consider
  ``adversarial soundness for Bloom filters'', but I assert that it
  isn't clear that their syntax allows them to study Bloom filters at all.}
  \jnote{I'm a little concerned about walking the line between
  criticizing them and offending them. I also wouldn't say ``their
  syntax doesn't allow them to study Bloom filters''; is that
  because they don't deal with random oracles?}
We give a more detailed comparison to, and criticism
of~\cite{naor2015bloom} in Appendix~\ref{sec:xxx}. \jnote{Any
comparison/criticism should be in the Intro. The Appendix is just a
technical comparison of different styles of definition.}

@@

\heading{Related work.} \jnote{See the discussion of related work in
Naor-Yogev. We should cite [LN93]. I can't tell how relevant [MNS11]
is. [HW13] seems relevant, though I don't think it is captured by
our current definitions.}

>>>>

\heading{Comparison to~\cite{naor2015bloom}.} Naor and
Yogev~\cite{naor2015bloom} recently considered the problem of
adversarial soundness for Bloom filters and, indeed,
their work served as inspiration for our own. Our work extends
their work significantly in several directions. For starters, we
consider abstract data structures (rather than only the case of
set-membership data structures), and consider privacy in addition to
soundness. Even with respect to the specific case of soundness for
set-membership data structures, our work offers several advantages
to the Naor-Yogev treatment:
\begin{itemize}
\item We explicitly distinguish between public and private
    portions of a data structure, something that was left
    ambiguous in~\cite{naor2015bloom}. This allows us, for
    example, to distinguish between the hash-function keys and
    the bit array when discussing classical Bloom filters.
\item The Naor-Yogev definition of soundness allows the
    adversary to make several set-membership queries, some of
    which may produce incorrect results, and the attacker then
    succeeds if it can output a \emph{fresh} query which leads
    to an error. We propose instead what we find to be a more
    natural definition in which the attacker succeeds if it can
    cause a certain number of incorrect results.
\item Naor and Yogev analyze a new Bloom-filter construction of
    their own design. In contrast, we are interested in
    analyzing practical constructions that have been proposed in
    prior work to understand how secure they are. In particular,
    we analyze Bloom filters in the random-oracle model.
    \jnote{Which are widely used?}
\end{itemize}
\tsnote{I think we can say a bit more here about what they show, and
  why their presentation is lacking, certainly as a work that anchors
  an important area of study.  This feels a bit weak, at the moment.
  For example, at the opening of this section we say they consider
  ``adversarial soundness for Bloom filters'', but I assert that it
  isn't clear that their syntax allows them to study Bloom filters at all.}
  \jnote{I'm a little concerned about walking the line between
  criticizing them and offending them. I also wouldn't say ``their
  syntax doesn't allow them to study Bloom filters''; is that
  because they don't deal with random oracles?}
We give a more detailed comparison to, and criticism
of~\cite{naor2015bloom} in Appendix~\ref{sec:xxx}. \jnote{Any
comparison/criticism should be in the Intro. The Appendix is just a
technical comparison of different styles of definition.}

@@

\heading{Related work.} 
\input{related-work}
\jnote{See the discussion of related work in
Naor-Yogev. We should cite [LN93]. I can't tell how relevant [MNS11]
is. [HW13] seems relevant, though I don't think it is captured by
our current definitions.}
